Implications of afforestation policies for global markets

### 2023-05-31 paper.Rmd
Update paper.Rmd

The global gains that can be realized from afforestion, however, are uncertain, with estimates ranging from 42 gigatonnes [@veldman2019] to 205 gigatonnes [@bastin2019], as afforestation appears to not provide the same benefits in all regions of the world. In particular, boreal forests appear to provide the smallest net benefits, as the carbon sequestrations benefits of conifer forests are mitigated by the reduction in albedo in winter [@mykleby2017] [@li2015]. That contrasts with the results for tropical forests where forests there provide a cooling impact due to changes in both albedo and evapotranspiration [@li2015].

>>>>

The global gains that can be realized from afforestion, however, are uncertain, with estimates ranging from 42 gigatonnes [@veldman2019] to 205 gigatonnes [@bastin2019], as afforestation appears to not provide the same benefits in all regions of the world. In particular, boreal forests appear to provide the smallest net benefits, as the carbon sequestrations benefits of conifer forests are mitigated by the reduction in albedo in winter [@mykleby2017] [@li2015]. Moreover, coniferous forests have been shown to increase soil organic carbon less than broadleaf forests [@guo2021]. With tropical forests, a strong positive result is derived from afforestation, as the carbon sequestration benefits is complemented by a cooling impact due to changes in both albedo and evapotranspiration, and with temperate forests, the impact of afforestation is shown to be positive, but less strongly so, due to a winter warming effect [@li2015].
